\bibitem{Harrison-2023}
Mark W. Harrison. ``Napoleon's Campaign in Egypt and Syria''. World History Encyclopedia, 27 April, 2023, \url{https://www.worldhistory.org/Napoleon's_Campaign_in_Egypt_and_Syria/}. Accessed 26 February 2025.

\bibitem{BM-RS-17}
British Museum. ``Everything you ever wanted to know about the Rosetta Stone''. British Museum blog, 14 July. 2017, \url{https://www.britishmuseum.org/blog/everything-you-ever-wanted-know-about-rosetta-stone}. Accessed 14 February 2025.

\bibitem{SH-Museum-24}
Shanghai Museum. ``On top of the pyramid, the civilization of ancient Egypt''. Shanghai Painting and Calligraphy Publishing House, 2024. ISBN: 9787547933831. p114.

\bibitem{LeVeque-Smith-25}
LeVeque, William Judson, Smith, David Eugene. ``numerals and numeral systems''. Encyclopedia Britannica, 7 Jan. 2025, \url{https://www.britannica.com/science/numeral}. Accessed 14 February 2025.

\bibitem{Clawson-1994}
Calvin C Clawson. ``The Mathematical Traveler, Exploring the Grand History of Numbers''. Springer. 1994, ISBN: 9780306446450

\bibitem{Noguchi2007}
Tetunori Noguti. ``数学的センスが身につく練習帳''. SoftBank Creative. 2007. ISBN: 9784797339314

\bibitem{HanXueTao2009}
Xuetao Han. ``好的数学——“下金蛋”的数学問題''. HuNan science and technology press. 2009, ISBN: 9787535756725

\bibitem{MacTutor-Brahmagupta-2000}
J J O'Connor and E F Robertson. ``Brahmagupta''. MacTutor, \url{https://mathshistory.st-andrews.ac.uk/Biographies/Brahmagupta/}. Accessed 10 March 2025.

\bibitem{Britannica-25}
The Editors of Encyclopaedia Britannica. ``al-Khwārizmī''. Encyclopedia Britannica, 13 Feb. 2025, \url{https://www.britannica.com/biography/al-Khwarizmi}. Accessed 18 February 2025.

\bibitem{Gies-Carney-24}
Gies, Frances Carney. ``Fibonacci''. Encyclopedia Britannica, 2 December 2024, \url{https://www.britannica.com/biography/Fibonacci}. Accessed 18 February 2025.
