\bibitem{Harrison-2023}
Mark W. Harrison. ``Napoleon's Campaign in Egypt and Syria''. World History Encyclopedia, 27 April, 2023, \url{https://www.worldhistory.org/Napoleon's_Campaign_in_Egypt_and_Syria/}. Accessed 26 February 2025.

\bibitem{BM-RS-17}
British Museum. ``Everything you ever wanted to know about the Rosetta Stone''. British Museum blog, 14 July. 2017, \url{https://www.britishmuseum.org/blog/everything-you-ever-wanted-know-about-rosetta-stone}. Accessed 14 February 2025.

\bibitem{SH-Museum-24}
上海博物馆. ``金字塔之颠：古埃及文明''. 上海书画出版社, 2024. p114. %ISBN: 9787547933831
%``On top of the pyramid, the civilization of ancient Egypt''

\bibitem{LeVeque-Smith-25}
LeVeque, William Judson, Smith, David Eugene. ``numerals and numeral systems''. Encyclopedia Britannica, 7 Jan. 2025, \url{https://www.britannica.com/science/numeral}. Accessed 14 February 2025.

\bibitem{Clawson-1994}
[美]\ 卡尔文$\cdot$C$\cdot$克劳森\ 著\ 袁向东、袁钧\ 译. ``数学旅行家：漫游数王国'' [M]. 上海教育出版社. 2001. %ISBN: 7-5320-7883-3/G $\cdot$ 7972

\bibitem{Noguchi2007}
[日] 野口哲典 著，刘慧 韩丽红 译. 数学原来可以这样学 [M]. 湖南人民出版社. 2014. p31. %ISBN: 9787556100897

\bibitem{HanXueTao2009}
韩雪涛. 好的数学——“下金蛋”的数学问题 [M]. 长沙：湖南科学技术出版社, 2009. p23. %ISBN: 9787535756725

\bibitem{MacTutor-Brahmagupta-2000}
J J O'Connor and E F Robertson. ``Brahmagupta''. MacTutor, \url{https://mathshistory.st-andrews.ac.uk/Biographies/Brahmagupta/}. Accessed 10 March 2025.

\bibitem{Britannica-25}
The Editors of Encyclopaedia Britannica. ``al-Khwārizmī''. Encyclopedia Britannica, 13 Feb. 2025, \url{https://www.britannica.com/biography/al-Khwarizmi}. Accessed 18 February 2025.

\bibitem{Gies-Carney-24}
Gies, Frances Carney. ``Fibonacci''. Encyclopedia Britannica, 2 Dec. 2024, https://www.britannica.com/biography/Fibonacci. Accessed 18 February 2025.

%% \bibitem{wiki-number}
%% Wikipedia. ``古代计数系统的历史''. \url{https://en.wikipedia.org/wiki/History_of_ancient_numeral_systems}


%% \bibitem{wiki-babylonian-num}
%% Wikipedia. ``古巴比伦数字''. \url{https://en.wikipedia.org/wiki/Babylonian_numerals}
