\bibitem{HanXueTao2012}
Xuetao Han. ``好的數學——方程的故事 (Story of equations)''. Hunan technology press, China. 2012. ISBN: 9787535770066

\bibitem{MacTour-Tartaglia}
J J O'Connor, E F Robertson. ``Tartaglia.'' MacTour. St Andrews University, Scotland. (2005-9) [2025-8-24]. \url{https://mathshistory.st-andrews.ac.uk/Biographies/Tartaglia}

\bibitem{Strick-2012}
Heinz Klaus Strick. ``Cardano and Tartaglia.'' Leverkusen. (2012) [2025-8-24]. \url{https://mathshistory.st-andrews.ac.uk/Strick/tartaglia.pdf}

\bibitem{MacTour-Tartaglia-Cardan}
J J O'Connor, E F Robertson. ``Tartaglia vs. Cardano.'' MacTour. St Andrews University, Scotland. (2005-9) [2025-8-24]. \url{https://mathshistory.st-andrews.ac.uk/HistTopics/Tartaglia_v_Cardan} %% source of example questions (about cubic equations) for challenge

\bibitem{OMerino-2006}
Orlando Merino. ``A Short History of Complex Numbers.'' University of Rhode Island. (2006-1) [2025-8-25]. \url{https://www.math.uri.edu/~merino/spring06/mth562/ShortHistoryComplexNumbers2006.pdf}.

\bibitem{MacTour-Bombelli}
J J O'Connor, E F Robertson. ``Bombelli.'' MacTour. St Andrews University, Scotland. (2000-1) [2025-9-8]. \url{https://mathshistory.st-andrews.ac.uk/Biographies/Bombelli/}

\bibitem{MacTour-Argand}
J J O'Connor, E F Robertson. ``Argand.'' MacTour. St Andrews University, Scotland. (2019-11) [2025-9-10]. \url{https://mathshistory.st-andrews.ac.uk/Biographies/Argand/}

\bibitem{Weisstein-2025}
Weisstein, Eric W. ``Argand Diagram.'' MathWorld, Wolfram Resource. (2025-9-9) [2025-9-14]. \url{https://mathworld.wolfram.com/ArgandDiagram.html}.

\bibitem{MacTour-dAlembert}
J J O'Connor, E F Robertson. ``Jean Le Rond d'Alembert.'' MacTour. St Andrews University, Scotland. (1998-10) [2025-9-14]. \url{https://mathshistory.st-andrews.ac.uk/Biographies/DAlembert/}

\bibitem{Ronald-2024}
Grimsley, Ronald. ``Jean Le Rond d'Alembert.'' Encyclopedia Britannica. (2024-11-13) [2025-9-14]. \url{https://www.britannica.com/biography/Jean-Le-Rond-dAlembert}.

\bibitem{MacTour-e}
J J O'Connor, E F Robertson. ``The number $e$.'' MacTour. St Andrews University, Scotland. (2001-9) [2025-9-16]. \url{https://mathshistory.st-andrews.ac.uk/HistTopics/e/}

\bibitem{Amerson-2021}
Emily Amerson. ``The Historical Development of the Number e.'' Math Virtual Tutor, LLC. Math History. (2021-8-27) [2025-9-16]. \url{https://mathvirtualtutor.com/the-historical-development-of-the-number-e}

\bibitem{Descartes-1638}
Shirley B. Gray, Jonathan Sahagun, and Cye Waldman. ``The Folium of Descartes and his Equiangular Spiral.'' National Curve Bank. (2019) [2025-9-18]. \url{http://nationalcurvebank.org/tourist/descartes.html}

\bibitem{MacTour-Equiangular}
J J O'Connor, E F Robertson. ``Equiangular spiral.'' MacTour. St Andrews University, Scotland. (20010-9) [2025-9-16]. \url{https://mathshistory.st-andrews.ac.uk/Curves/Equiangular/}

\bibitem{MacTour-Bernoulli-tomb}
J J O'Connor, E F Robertson. ``Jacob Bernoulli's tomb in Basel.'' MacTour. St Andrews University, Scotland. (2021?) [2025-9-18]. \url{https://mathshistory.st-andrews.ac.uk/Extras/Bernoulli_tomb/}

\bibitem{Maor-2010}
Eli Maor. ``E: The Story of a Number.'' Princeton University Press. Feb. 2009. ISBN: 978-0691141343.

\bibitem{Weil-2024}
Gotthold Eisenstein. ``Mathematische Werke.'' American Mathematical Society. Oct. 1997. ISBN: 978-0828412803

\bibitem{Courant1969}
Richard Courant, Herbert Robbins, Reviewed by Ian Stewart. ``What Is Mathematics? An Elementary Approach to Ideas and Methods 2nd Edition.'' Oxford University Press, 1996, ISBN: 978-0195105193.
