\ifx\wholebook\relax \else

\documentclass[b5paper]{article}
\usepackage[nomarginpar
  %, margin=.5in
]{geometry}

\addtolength{\oddsidemargin}{-0.05in}
\addtolength{\evensidemargin}{-0.05in}
\addtolength{\textwidth}{0.1in}

\usepackage[en]{../prelude}

\setcounter{page}{1}

\begin{document}

\title{Numerals}

\author{Xinyu LIU
\thanks{{\bfseries Xinyu LIU} \newline
  Email: liuxinyu99@hotmail.com \newline}
  }

\maketitle
\fi

\markboth{Numerals}{A tour of numbers}

\ifx\wholebook\relax
\chapter{Numerals}
\fi

\epigraph{The total number of minds in the universe is one.}{Erwin Schrödinger}

Numbers appear everywhere in our daily life. Here's a piece of news pops up today: \textit{The 2024 Paris Olympic Games to an end on Sunday August 11, 2024. Paris is the second city, after London, to host the Summer Olympics three times. It set a record of gender equality, with 5,250 male and 5250 female athletes. In total, 32 sports and 329 events were featured, with 206 countries and regions participating. Four new sports made their debut: skateboarding, surfing, sport climbing, and breakdancing. A total of 329 gold medals were up for grabs. Athletes from various countries and regions demonstrated outstanding athleticism. The United States and China tied for the most gold medals, with each securing 40. The United States also led in silver medals with 44 and bronze medals with 42.} There are 14 numbers among 120 words.

\ifx\wholebook\relax \else
\section{Answer}
\shipoutAnswer

\begin{thebibliography}{99}

%% \bibitem{wiki-number}
%% Wikipedia. ``History of ancient numeral systems''. \url{https://en.wikipedia.org/wiki/History_of_ancient_numeral_systems}

%% \bibitem{Calvin-Clawson-1994}
%% Calvin C Clawson. ``The Mathematical Traveler, Exploring the Grand History of Numbers''. Springer. 1994, ISBN: 9780306446450

%% \bibitem{wiki-babylonian-num}
%% Wikipedia. ``Babylonian numerals''. \url{https://en.wikipedia.org/wiki/Babylonian_numerals}

\end{thebibliography}

\expandafter\enddocument
%\end{document}

\fi
